tester

### 2023-08-23 Manuscript.Rmd

The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).
All data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript), ensuring the reproducibility of our findings.

>>>>

## Data availability

The experimental procedure, power analyses to determine sample size and statistical approach were preregistered for both [experiment 1](https://osf.io/4xcn5/) and [experiment 2](https://osf.io/dhg8u/).

All raw data and code for the analysis are available in the [github repository](https://github.com/Body-Pain-Perception-Lab/tgi-spinal/tree/Markdown-manuscript). This, and a wiki guide to analysing the data, can be accessed through the project's [OSF page](https://osf.io/uyrtq/).

### 2023-08-23 old/testing.Rmd

model_cold_exp1 = glmmTMB::glmmTMB(beta ~ cold_probe *manipulation+trial_n+(1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold'),
                            na.action = na.omit,
                            contrasts=list(cold_probe = cold)

@@

```

>>>>

model_cold_exp1 = glmmTMB::glmmTMB(beta ~ cold_probe *manipulation+trial_n+(1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'cold'),
                            na.action = na.omit,
                            contrasts=list(cold_probe = cold))

@@

model_burn = glmmTMB::glmmTMB(beta ~ manipulation * cold_probe + trial_n +
                              (1|ID) + (1|order),
                            family = glmmTMB::beta_family(),
                            ziformula = ~1+manipulation,
                            data = df_long_exp1 %>% filter(quality == 'burn'),
                            na.action = na.omit)

plot(ggeffect(model_burn, terms = c("manipulation")))

quality = "burn"

meaneffects = df_long_exp1 %>% filter(quality == 'burn', beta != 0) %>% group_by(manipulation,cold_probe) %>% summarize(mean = mean(beta), se = sd(beta)/sqrt(n()))

plot2 = df_long_exp1 %>% filter(quality == 'burn', beta != 0) %>% group_by(ID, manipulation,cold_probe) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = cold_probe))+geom_point(position = position_dodge(width = 0.3))+
  geom_pointrange(data = meaneffects, aes(x = manipulation, col = cold_probe, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
  geom_line(
    data = meaneffects,
    aes(x = manipulation, y = mean, group = cold_probe, col = cold_probe),
    position = position_dodge(width = 0.5),
    size = 1.2)+ggtitle("Without 0")

meaneffects2 = df_long_exp1 %>% filter(quality == 'burn') %>% group_by(manipulation,cold_probe) %>% summarize(mean = mean(beta, na.rm = T), se = sd(beta, na.rm =T)/sqrt(n()))

plot1 = df_long_exp1 %>% filter(quality == 'burn') %>% group_by(ID, manipulation,cold_probe) %>% summarize(mean = mean(beta)) %>% ggplot(aes(x = manipulation, y = mean, col = cold_probe))+geom_point(position = position_dodge(width = 0.3))+
  geom_pointrange(data = meaneffects2, aes(x = manipulation, col = cold_probe, y = mean, ymin = mean-2*se, ymax = mean+2*se), size = 0.5, linewidth = 1.5,position = position_dodge(width = 0.5))+theme_classic()+
  geom_line(
    data = meaneffects2,
    aes(x = manipulation, y = mean, group = cold_probe, col = cold_probe),
    position = position_dodge(width = 0.5),
    size = 1.2)+ggtitle("With 0")

plot1+plot2
```
